%-------------------------------------------------------------------------------
% work experience
%-------------------------------------------------------------------------------

\begin{section}[Experience]

  % \entry%
  % {Economic Researcher and Teacher} % Job Title
  % {University of Zurich} % Organization
  % {Zurich, CH} % Location
  % {2015 - to date} % Date
  % {% Additional Information
  %   \begin{entrylist}
  %     \item Conducted research in behavioral economics
  %     \item Designed and conducted economic experiments
  %     \item Performed causal and predictive analysis \\ (e.g. regression, fixed-effects, heterogeneity analysis, cluster analysis, local regression, model selection, equilibria simulation)
  %     \item Presented at local and international scientific meetings
  %     \item Represented PhD candidates on the department and university level
  %     \item Co-lead and taught for \href{https://pp4rs.github.io/}{\faIcon{link} Programming Practices for Economists} and instructed for \href{https://uzhcrs.github.io/2019-02-07-zurich/}{\faIcon{link} Software Carpentry}
  %     \item Currently writing a \href{https://lachlandeer.github.io/snakemake-econ-r-tutorial/}{\faIcon{link} web tutorial} on scalable and reproducible economic research workflow management
  %     \item Teaching assistance for Advanced Microeconomics I and II
  %   \end{entrylist}
  % }%

  \entry%
    {Senior Data Scientist} % Job Title
    {Tourlane} % Organization
    {Berlin, DE} % Location
    {Since July 2022} % Date
    {% Additional Information
    \begin{entrylist}
      \item Responsible for all data science projects in the company and leading a team of two data scientists.
      \item Leading core company wide initiative to improve the scalability of the sales funnel through improved data collection, utilization, and live prediction models.
    \end{entrylist}
    }%

  \entry%
    {Data Scientist} % Job Title
    {Tourlane} % Organization
    {Berlin, DE} % Location
    {2021 - 2022} % Date
    {% Additional Information
    \begin{entrylist}
      \item Developed and brought a live customer segmentation machine learning model into production. The model increased company revenue by 500.000 EUR and company profits by 40.000 EUR during the AB test and is in production today.
      \item Decreased runtime of AB tests by 75\% through use of more efficient statistical tests and unification of treatment groups.
      \item Improved detection of repeating customers by 25\%.
      \item Reduced data warehouse runtime by 50\% and runtime of main table from 20 minutes to 90 seconds through code optimization.
      \item Interviewed new colleagues and mentored data analysts on coding best practices, version control, statistics.
    \end{entrylist}
    }%

  \entry%
    {Intern Strategic Procurement} % Job Title
    {Daimler AG} % Organization
    {Sindelfingen, DE} % Location
    {2011 - 2012} % Date
    {% Additional Information
     Co-developed the design of two procurement auctions which were used to buy the steel for the 2012 C-Class.
    }%
\end{section}

